### 2013-05-16 Docs/architecture/architecture.tex
fix

The routines in {\tt AstroDev/initial\_models/}\footnote{The {\tt \astrodev} package is currently distributed separately from \maestro} prepare an initial model
for \maestro.  There are two types of routines here, the first type
modify an existing 1D initial model produced somewhere else (e.g.\ a
1D stellar evolution code), and map it onto a uniform grid, at
the desired resolution, using the equation of state in \maestro, and
using \maestro's discretization of hydrostatic equilibrium.  The second
type generate the initial model internally, by integrating the
condition of hydrostatic equilibrium together with a simplifying
assumption on the energy (e.g. isothermal or isentropic).  In
both cases hydrostatic equilibrium is enforced as:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}
Here, $g_{i+1/2}$ is the edge-centered gravitational acceleration.

>>>>

The routines in {\tt Util/initial\_models/} prepare an initial model
for \maestro.  In general, there are two different proceduces that are
needed.  The first type modify an existing 1D initial model produced
somewhere else (e.g.\ a 1D stellar evolution code), and map it onto a
uniform grid, at the desired resolution, using the equation of state
in \maestro, and using \maestro's discretization of hydrostatic
equilibrium.  The second type generate the initial model internally,
by integrating the condition of hydrostatic equilibrium together with
a simplifying assumption on the energy (e.g. isothermal or
isentropic).  In both cases hydrostatic equilibrium is enforced as:
\begin{equation}
\frac{p_{i+1} - p_i}{\Delta r} = \frac{1}{2} (\rho_i + \rho_{i+1})
g_{i+1/2}
\end{equation}
Here, $g_{i+1/2}$ is the edge-centered gravitational acceleration.
